Who introduced the bug? The importance of the previous commit

### 2016-01-28 paperMSR.tex
RQ1 and RQ2

When a failure is found in the behavoir of a software, the developers try to fix it locating and modifiying the line/s that contains the bug in the source code. It seems reasonable to assign the previous modification of this/those lines, \textit{The previous commit}, as the cause of the bug. But in fact, find when and where a bug was injected into the souce code is not a trivial task which has largely been ignored due to the data related about the origin of a bug is embedded in the evolution of the software \cite{sinha2010buginnings}.

In spite of some studies in bug seeding start with this implicit assumption, \textit{"This earlier change is the one that caused the later fixed"} \cite{williams2008szz} or even we can find this assumption in tools that prevent for future bugs; \textit{" We assume that a change/commit is buggy if its modifications has been later altered by a bug-fix commit"} \cite{fejzer2015supporting}. We think that there is not empirical evidence supporting this assumption and we conducted an observational study on fix-bugs, expend significantly effort locating the bug origins into the source code.

@@

In this paper, we attempt to address the following research question regarding who introduced the bug in the source code.
\begin{itemize}
    %\item RQ1 : How can tickets which are bug reports be differentiated from those that are not?
     \item RQ1:  How I can know that a change was done to fix a bug in the source code? How I can identify them?
    %\item RQ2:  How often is the bug caused in the previous commit?
     \item RQ2:  In which cases the previous commit/s are responsible to cause the bug?
\end{itemize}

@@

\section{Discussion}
\label{sec:discussion}
\fbox{\begin{minipage}{25em}
\textbf{RQ1:} asdasdasdasdasdasdsaddasdadasdasd
\end{minipage}}
\fbox{\begin{minipage}{25em}
\textbf{RQ2:} asdasdasdasdasdasdsaddasdadasdasd
\end{minipage}}
- Como se responden las RQ1 y RQ2
- No todos los casos son tan claros como los mostrados en los ejemplos ....
- Casuistica del common juidment
- Hemos sido conservadores
-Hemos utilizado la herramienta porque es un proceso complicado
Once we have all the tickets analyzed by diferents researchers who have used a double blind, how to proceed if there are discordances between them:
\begin{enumerate}
\item Should they discuss after their analysis to reach a better classification?, Should the tool provide this?
\item Does the Bug report only the same ticket classified as Bug report for all the researchers?
\end{enumerate}

>>>>

When a failure is found in the behavoir of a software, the developers try to fix it locating and modifiying the line that contains the bug in the source code. It seems reasonable to assign the previous modification of this line as the cause of the bug, this previous modification is \textit{The previous commit}. But in fact, find when and where a bug was injected into the souce code is not a trivial task which has largely been ignored due to the data related about the origin of a bug is embedded in the evolution of the software \cite{sinha2010buginnings}.

In spite of some studies in bug seeding start with this implicit assumption, \textit{"This earlier change is the one that caused the later fixed"} \cite{williams2008szz} or \textit{"The lines affected in the process of fixing a bug are the same one that originated or seeded that bug"} \cite{izquierdo2011developers}.Even, we can find this assumption in tools that prevent for future bugs; \textit{"We assume that a change/commit is buggy if its modifications has been later altered by a bug-fix commit"} \cite{fejzer2015supporting}. We think that there is not empirical evidence supporting this assumption and we conducted an observational study on fix-bugs, expend significantly effort locating the bug origins into the source code.

@@

In this paper, we attempt to address the following research question regarding who introduced the bug in the source code.
\begin{itemize}
    %\item RQ1 : How can tickets which are bug reports be differentiated from those that are not?
     \item RQ1:  How I can know that a change was done to fix a bug in the source code? How I can identify them?
    %\item RQ2:  How often is the bug caused in the previous commit?
     \item RQ2:  In which cases the previous commit/s inserted the line with the bug into the source code?
\end{itemize}

@@

\section{Discussion}
\label{sec:discussion}
\fbox{\begin{minipage}{25em}
\textbf{RQ1: Using all the information available in the bug tracking system and code review system related a fix-bug, we have obtained that this fix-bug were real Bug Reports in a 72\% of the tickets analyzed} 
\end{minipage}}
\fbox{\begin{minipage}{25em}
\textbf{RQ2: We have comfirmed that 50\% of the previous commits analyzed caused the failure in the system, whereas the 37\% of them didn't injected any bug in the code source } 
\end{minipage}}
\\
- No todos los casos son tan claros como los mostrados en los ejemplos ....
- Casuistica del common juidment
- Hemos sido conservadores
-Hemos utilizado la herramienta porque es un proceso complicado
Once we have all the tickets analyzed by diferents researchers who have used a double blind, how to proceed if there are discordances between them:
\begin{enumerate}
\item Should they discuss after their analysis to reach a better classification?, Should the tool provide this?
\item Does the Bug report only the same ticket classified as Bug report for all the researchers?
\end{enumerate}
